The Calculus of Linear Constructions

### 2021-10-15 writing/draft2.tex
wip

>>>>

  \section{CLC in Action}

  \subsection{Inductive Types}
  A core design goal of CLC is to support an ergonomic interface for users to define both non-linear and linear inductive types. Inductive data should be both easy to construct, and to eliminate. The ! exponential, or its adjoint alternatives often get in the way of directly using data. Due to CLC's usage of universe sorts instead of !, data construction and elimination becomes much.

  \subsection{Resource Reasoning}
  \subsection{Parametric Reasoning}
  \subsection{Mutable Data Structures}
  \subsection{Continuations}
  \subsection{Program Synthesis}
